---
title: "My Lab Report knitr"
author: "Binita Wosti"
date: "2026-02-14"
output:
  word_document: default
  html_document: default
---

library("ggplot2")

#0. codes in chunks #0.1 for loading data
```{r}
data(mtcars)
```

#0.2 show the first few rows of data
```{r}
head(mtcars)
```
#1. Summary of data/ default is TRUE
```{r}
summary(mtcars)
```

#2.Summary without showing code
```{r echo=FALSE}
summary(mtcars)
```

#3.Summary with code excecution and result shows
```{r eval=TRUE}
summary(mtcars)
```

#4. Summary (stops code execution but still shows code, but output won’t be shown)
```{r eval= FALSE}
summary(mtcars)
```


#5. showing both code and output /default is TRUE
```{r inclue= TRUE}
summary(mtcars)
```

#6. The chunk is hidden bcz {r include=FALSE}
```{r include = FALSE}
summary(mtcars)
```

#7. Shows warning/Default is TRUE
```{r warning=TRUE}
log(-1)
```

#8. Does not show warning
```{r warning=FALSE}
log(-1)
```

#9. Plot dimension in inches 
```{r fig.width=8, fig.height=6}
plot(cars)
```

#10. Add caption to plot
```{r fig.cap="Scatter plot of cars data"}
plot(cars)
```

#11. Combine both
```{r fig.width=10, fig.height=5, fig.cap="Updated car plot"}
plot(cars)
```

#12. Plot (Violin plot) with code - mpg data
```{r}
library(ggplot2)
ggplot(mpg, aes(drv, cty, colour = class)) +
geom_violin() +
labs(x = "Drive Type",
    y = "City Mileage",
    title = "City Mileage by Drive Type")+
theme_bw() +
  theme(
    legend.position = "right",
    legend.key.size = unit(0.2, "cm"),
    axis.title = element_text(size = 15),   
    axis.text.x = element_text(size = 12, angle = 45, hjust =1),    
    panel.grid.major = element_blank(),     
    panel.grid.minor = element_blank()        
  )
```

#13. Plot without showing code/adding library(ggplot2) is additional 
```{r echo=FALSE}
library(ggplot2)
ggplot(mpg, aes(drv, cty, colour = class)) +
geom_violin() +
labs(x = "Drive Type",
    y = "City Mileage",
    title = "City Mileage by Drive Type")+
theme_bw() +
  theme(
    legend.position = "right",
    legend.key.size = unit(0.2, "cm"),
    axis.title = element_text(size = 15),   
    axis.text.x = element_text(size = 12, angle = 45, hjust =1),    
    panel.grid.major = element_blank(),     
    panel.grid.minor = element_blank()        
  )
```